Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-13 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Add text to paper draft

We collected "best tracks" data on hurricane tracks for Atlantic basin storms between 1988 and 2014 from the extended best tracks database. ... This data gives time stamps for each observation in UTC.

These data typically give measurements of storm center location at 6-hour intervals. We interpolated these location values to every 15 minutes during the period when the storm was active, using a linear interpolation between each measured point.

@@

@@

@@

>>>>

We collected "best tracks" data on hurricane tracks for Atlantic basin storms between 1988 and 2014 from the extended best tracks database. This dataset is based on a poststorm assessment of each storm conducted by the United States National Hurricane Center (NHC) and incorporates data from a variety of sources, including satellite data and, when available, aircraft reconnaisance data [@Landsea2013]. This data gives time stamps for each observation in Coordinated Universal Time (UTC; also known as Zulu Time, sometimes indicated by "Z").

These data typically give measurements of storm center location at 6-hour intervals, at synoptic times (i.e., 6:00 am, 12:00 pm, 6:00 pm, and 12:00 am UTC); some landfalling storms have an additional observation at the time of landfall [@Landsea2013]. These positions are given to within 0.1 degrees latitude / longitude at these synoptic times [@Landsea2013]. We interpolated these location values to every 15 minutes during the period when the storm was active, using a linear interpolation between each measured point.

@@

These wind models use estimates of maximum wind speed from the best tracks dataset. These maximum wind speed estimates in the best tracks dataset are rounded to 5-knot intervals and is the maximum 1-minute-average windspeed at 10 meters above the ground [@Landsea2013]. This windspeed is typically determined using the Dvorak technique to estimate windspeed from satellite measurements, although data from aircraft reconnaisance in also sometimes incorporated in the estimate [@Levinson2010].

@@

There is some uncertainty in the position estimates from the best tracks hurricane dataset, since the estimation of storm position for best tracks data involes a poststorm subjective smoothing and integration of many different types of data [@Landsea2013]. In a survey of researchers who perform the poststorm data aggregation to create the best tracks datasets, uncertainty in the center position of a US landfalling storm in the "best tracks" dataset was estimated at approximately 8 nautical miles for major hurricanes, 11 nautical miles for Category 1 and 2 hurricanes, and 15 nautical miles for tropical storms [@Landsea2013]. Uncertainty in estimates of a storm's position also varies by time of day, with more certain estimates during daylight than during the night [@Landsea2013].

@@

There is some uncertainty in the maximum wind speed values estimated at each synoptic time for each storm. For US landfalling storms, the estimate of storm intensity in the best tracks dataset is estimated to have an uncertainty of around 8 knots for tropical storms, 10 knots for Category 1 and 2 hurricanes, and 13 knots for major hurricanes [@Landsea2013]. Since the wind model used here uses these best tracks maximum wind speeds as an input, this uncertaintly would propogate into our estimates of windspeed within each county for each storm.

### 2016-06-13 writing/DraftExposurePaper/DraftExposurePaper.tex
Add text to paper draft

We collected ``best tracks'' data on hurricane tracks for Atlantic basin
storms between 1988 and 2014 from the extended best tracks database.
\ldots{} This data gives time stamps for each observation in UTC.

These data typically give measurements of storm center location at
6-hour intervals. We interpolated these location values to every 15
minutes during the period when the storm was active, using a linear
interpolation between each measured point.

@@

@@

@@

@@

>>>>

We collected ``best tracks'' data on hurricane tracks for Atlantic basin
storms between 1988 and 2014 from the extended best tracks database.
This dataset is based on a poststorm assessment of each storm conducted
by the United States National Hurricane Center (NHC) and incorporates
data from a variety of sources, including satellite data and, when
available, aircraft reconnaisance data (Landsea and Franklin 2013). This
data gives time stamps for each observation in Coordinated Universal
Time (UTC; also known as Zulu Time, sometimes indicated by ``Z'').

These data typically give measurements of storm center location at
6-hour intervals, at synoptic times (i.e., 6:00 am, 12:00 pm, 6:00 pm,
and 12:00 am UTC); some landfalling storms have an additional
observation at the time of landfall (Landsea and Franklin 2013). These
positions are given to within 0.1 degrees latitude / longitude at these
synoptic times (Landsea and Franklin 2013). We interpolated these
location values to every 15 minutes during the period when the storm was
active, using a linear interpolation between each measured point.

@@

These wind models use estimates of maximum wind speed from the best
tracks dataset. These maximum wind speed estimates in the best tracks
dataset are rounded to 5-knot intervals and is the maximum
1-minute-average windspeed at 10 meters above the ground (Landsea and
Franklin 2013). This windspeed is typically determined using the Dvorak
technique to estimate windspeed from satellite measurements, although
data from aircraft reconnaisance in also sometimes incorporated in the
estimate (Levinson et al. 2010).

@@

There is some uncertainty in the position estimates from the best tracks
hurricane dataset, since the estimation of storm position for best
tracks data involes a poststorm subjective smoothing and integration of
many different types of data (Landsea and Franklin 2013). In a survey of
researchers who perform the poststorm data aggregation to create the
best tracks datasets, uncertainty in the center position of a US
landfalling storm in the ``best tracks'' dataset was estimated at
approximately 8 nautical miles for major hurricanes, 11 nautical miles
for Category 1 and 2 hurricanes, and 15 nautical miles for tropical
storms (Landsea and Franklin 2013). Uncertainty in estimates of a
storm's position also varies by time of day, with more certain estimates
during daylight than during the night (Landsea and Franklin 2013).

@@

There is some uncertainty in the maximum wind speed values estimated at
each synoptic time for each storm. For US landfalling storms, the
estimate of storm intensity in the best tracks dataset is estimated to
have an uncertainty of around 8 knots for tropical storms, 10 knots for
Category 1 and 2 hurricanes, and 13 knots for major hurricanes (Landsea
and Franklin 2013). Since the wind model used here uses these best
tracks maximum wind speeds as an input, this uncertaintly would
propogate into our estimates of windspeed within each county for each
storm.

@@

\hypertarget{ref-Landsea2013}{}
Landsea, Christopher W., and James L. Franklin. 2013. ``Atlantic
Hurricane Database Uncertainty and Presentation of a New Database
Format.'' \emph{Monthly Weather Review} 141: 3576--92.

\hypertarget{ref-Levinson2010}{}
Levinson, David H., Howard J. Diamond, Kenneth R. Knapp, Michael C.
Kruk, and Ethan J. Gibney. 2010. ``Toward a Homogenous Global Tropical
Cyclone Best-Track Dataset.'' \emph{American Meteorological Society} x:
377--80.
doi:\href{https://doi.org/10.1175/2010BAMS2930.1}{10.1175/2010BAMS2930.1}.
